---
title: "Results of Logarithmic encoding model"
author: "Xiuna Zhu"
date: "1/9/2021"
output:
  html_document:
    df_print: paged
    number_sections: true
  pdf_document: 
    number_sections: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# load packages and functions {-}
```{r include=FALSE}
library(rlist)
library(ez)
library(tidyverse)
library(latex2exp)
library(lsr)
library(rticles)
library(DescTools)
library(heplots)
library(lme4)
library(rstatix)
library(boot)
library(ggpubr)
library(reshape2)
source('mytheme.R')
# model version
modelversion = 'log_rstan'
rstanmodelPath = 'modelrlt'
modelPath = paste0(rstanmodelPath, '/models/', modelversion)
```


# Merge the model Result data{-}
```{r include=FALSE}
#To preprocess the model result data, and merge different model version data together.
#function to merge the model result data
funMergeMRlt <- function(explist, path, version){
  rltfilename <- {}
  rltfilename <- c(rltfilename, paste0("rlt_", explist, ".rds"))
  Bayparlist <- {}
  AllDat_predY <- {}
  AllDat_newY <- {}
  modelResultAll <- list()
  merge.data.all <- {}
  merge.data <- readRDS(file.path(paste0( getwd(), "/", path, "/rlt/", rltfilename[1])))
  for (i in 1:length(merge.data)){
    modelResultAll <- list.append(modelResultAll, merge.data[[i]])
    Bayparlist <- rbind(Bayparlist, merge.data[[i]]$Baypar)
    AllDat_predY <- rbind(AllDat_predY, merge.data[[i]]$PredY_list)
    AllDat_newY<- rbind(AllDat_newY, merge.data[[i]]$NewY_list)
  }
  
  if (length(rltfilename) >= 2) {
    for (i in 2:length(rltfilename)){
      new.data = readRDS(file.path(paste0(getwd(), "/", path, "/rlt/", rltfilename[i])))
      for (j in 1:length(new.data)){
        modelResultAll <- list.append(modelResultAll, new.data[[j]])
        Bayparlist <- rbind(Bayparlist, new.data[[j]]$Baypar)
        AllDat_predY <- rbind(AllDat_predY, new.data[[j]]$PredY_list)
        AllDat_newY<- rbind(AllDat_newY, new.data[[j]]$NewY_list)
      }
    }
  }
  write.csv(Bayparlist, paste0(getwd(), "/", path, "/rlt/AllDat_Bayparlist_", modelversion, ".csv"))
  write.csv(AllDat_predY, paste0( getwd(), "/",path, "/rlt/AllDat_predY_", modelversion, ".csv"))
  write.csv(AllDat_newY, paste0(getwd(), "/",path, "/rlt/AllDat_newY_", modelversion, ".csv"))
}

funMergeMRlt(c('Exp1','Exp2','Exp3','Exp4') , modelPath, modelversion)
```

# Corrct rate
```{r include=FALSE}
## read data
dat = data.frame()
readCSV <- function(fn){
  filename = paste0("../data/","Exp",toString(fn),".csv")
  read.csv(filename) %>% mutate(Exp = fn)
}

dat <- map_df(1:4, readCSV)
dur <- sort(unique(dat$curDur))
AllExpData <- dat %>% filter(valid == 1)
AllExpData$Exp = paste0('Exp', AllExpData$Exp)

#plot WM correct rates

AllExpData$WMCrr <- AllExpData$TPresent == AllExpData$WMRP
wmPlotData <- dplyr::group_by(AllExpData, Exp, WMSize, NSub) %>% 
  dplyr::summarize(m_WMCrr = mean(WMCrr), n = n(), se_WMCrr = sd(WMCrr)/sqrt(n-1))
wmPlotData%>%dplyr::group_by(Exp, WMSize)%>%
  dplyr::summarize( n = n(),
             mean_WMCrr = mean(m_WMCrr), se_WMCrr = sd(m_WMCrr)/sqrt(n-1) ) -> meanForPlot
```

```{r}
meanForPlot$WMSize <- factor(meanForPlot$WMSize, labels = c("low", "medium",  "high")) 
WMCrr2 <- ggplot(meanForPlot, aes(WMSize, mean_WMCrr, ymin = mean_WMCrr - se_WMCrr, ymax = mean_WMCrr + se_WMCrr,
                                  group =Exp, color = Exp, fill = Exp))+ 
  geom_line(stat = "identity",position = position_dodge(width = 0.2))+
  geom_point(stat = "identity",position = position_dodge(width = 0.2))+ 
  geom_errorbar(width=.2,  position = position_dodge(width = 0.2)) +
  coord_cartesian(ylim = c(0.5, 1)) +
  colorSet4+
  labs(x = "Memory load", y = "Mean accuracy in WM task") +
  theme_new 
WMCrr2
ggsave(paste0(getwd(), "/figures/WMCrr2.png"), WMCrr2, width = 5, height = 4)
```



```{r}
### generate WM correct rates
dat$WMCrr <- dat$TPresent == dat$WMRP
m_wmp<- dplyr::group_by(dat, Exp, WMSize, NSub) %>% 
  dplyr::summarize(m_WMCrr = mean(WMCrr), n =n(), se_WMCrr = sd(WMCrr)/sqrt(n-1))

```


# load model results

```{r include=FALSE}
### load parameters from model
Bayparlist <- read.csv(paste0(modelPath, "/rlt/AllDat_Bayparlist_",modelversion,".csv"))
Bayparlist$mu_pr = exp(Bayparlist$mu_pr_log + Bayparlist$sig_pr2_log^2*0.5)
Bayparlist$sig_pr2 = (exp(Bayparlist$sig_pr2_log^2)-1)*exp(2*Bayparlist$mu_pr_log+Bayparlist$sig_pr2_log^2)
```

```{r}
### Average Parameters 
mm_Baypar <- dplyr::group_by(Bayparlist, Exp) %>%
  dplyr::summarize( m_sig_s2 = mean(sig_s2),
                    m_sig_pr2_log = mean(sig_pr2_log),
                    m_ks= mean(ks), 
                    m_kr = mean(kr), 
                    m_ls = mean(ls), 
                    m_mu_pr_log= mean(mu_pr_log),
                    n= n(),
                    se_sig_s2 = sd(sig_s2)/sqrt(n-1),
                    se_sig_mn2 = sd(sig_mn2)/sqrt(n-1),
                    se_sig_pr2_log = sd(sig_pr2_log)/sqrt(n-1),
                    se_ks = sd(ks)/sqrt(n-1),
                    se_kr = sd(kr)/sqrt(n-1),
                    se_ls =sd(ls)/sqrt(n-1),
                    se_mu_pr_log = sd(mu_pr_log)/sqrt(n-1)) 
mm_Baypar
```


# Prediction results
```{r}
#load prediction
AllDat_predY <- read.csv(paste0(modelPath, "/rlt/AllDat_predY_",modelversion,".csv"))
AllDat_predY$WMSize <- as.factor(AllDat_predY$WMSize)
levels(AllDat_predY$WMSize) = c("low", "medium",  "high")
AllDat_predY$pred_Bias = AllDat_predY$mu_r - AllDat_predY$curDur
AllDat_predY$predErr = AllDat_predY$mu_r - AllDat_predY$repDur
AllDat_predY$relatErr = AllDat_predY$predErr / AllDat_predY$repDur
```

```{r}
#calculate the mean reproduction biases for the five given intervals for all subjects
mpredY_sub <- dplyr::group_by(AllDat_predY, curDur, Exp, NSub, WMSize) %>%
  dplyr::summarize(n = n(), 
                   m_repDur = mean(repDur), 
                   sd_repDur = sd(repDur),
                   m_mu_r = mean(mu_r),
                   m_sig_r = mean(sig_r),
                   m_wp = mean(wp),
                   se_wp = sd(wp)/sqrt(n-1),
                   log_lik =mean(log_lik),
                   cv =sd_repDur/ m_repDur,
                   pred_cv = mean(sig_r/mu_r),
                   predRP_err = mean(m_mu_r-m_repDur),
                   predVar_err = mean(m_sig_r-sd_repDur),
                   predRP_rerr = mean(abs(m_mu_r-m_repDur)/m_repDur),
                   predVar_rerr = mean(abs(m_sig_r-sd_repDur)/sd_repDur),
                   predcv_err = pred_cv-cv,
                   predcv_rerr = mean(abs(pred_cv-cv)/cv))

mpredY_sub_split <-split(mpredY_sub %>%select(c('Exp', 'NSub', 'WMSize', 'm_repDur', 'curDur')), mpredY_sub$curDur) 
mpredY_sub_cv_split <-split(mpredY_sub %>%select(c('Exp', 'NSub', 'WMSize', 'cv', 'curDur')), mpredY_sub$curDur) 

mpredY_sub_split1 <-split(mpredY_sub %>%select(c('Exp', 'NSub', 'WMSize', 'curDur' ,'m_repDur')), mpredY_sub$WMSize) 
mpredY_sub_cv_split1 <-split(mpredY_sub %>%select(c('Exp', 'NSub', 'WMSize','curDur', 'cv')), mpredY_sub$WMSize) 
mpredY_sub_jasp_RP = NULL
mpredY_sub_jasp_cv = NULL
mpredY_sub_jasp_RP1 = NULL
mpredY_sub_jasp_cv1 = NULL
for(i in 1: length(mpredY_sub_split)){
  temp = mpredY_sub_split[[i]]
  curDur = unique(temp$curDur)
  temp$curDur = NULL
  colnames(temp) = c('Exp', 'NSub', 'WMSize', paste0('m_repDur_', curDur))
  
  temp_cv = mpredY_sub_cv_split[[i]]
  curDur = unique(temp_cv$curDur)
  temp_cv$curDur = NULL
  colnames(temp_cv) = c('Exp', 'NSub', 'WMSize', paste0('cv_', curDur))
  if(i == 1){
    mpredY_sub_jasp_RP = temp
    mpredY_sub_jasp_cv = temp_cv
  }
  else{
    mpredY_sub_jasp_RP = left_join(mpredY_sub_jasp_RP, temp, by=c("Exp",  "NSub", "WMSize"))
    mpredY_sub_jasp_cv = left_join(mpredY_sub_jasp_cv, temp_cv, by=c("Exp",  "NSub", "WMSize"))
  }
  
}
for (i in 1: length(mpredY_sub_split1)){
  temp1 = mpredY_sub_split1[[i]]
  WMSize = unique(temp1$WMSize)
  temp1$WMSize = NULL
  colnames(temp1) = c('Exp', 'NSub', 'curDur', paste0('m_repDur_', WMSize))
  
  temp_cv1 = mpredY_sub_cv_split1[[i]]
  WMSize = unique(temp_cv1$WMSize)
  temp_cv1$WMSize = NULL
  colnames(temp_cv1) = c('Exp', 'NSub', 'curDur', paste0('cv_', WMSize))
  if(i == 1){
    mpredY_sub_jasp_RP1 = temp1
    mpredY_sub_jasp_cv1 = temp_cv1
  }
  else{
    mpredY_sub_jasp_RP1 = left_join(mpredY_sub_jasp_RP1, temp1, by=c("Exp",  "NSub", "curDur"))
    mpredY_sub_jasp_cv1 = left_join(mpredY_sub_jasp_cv1, temp_cv1, by=c("Exp",  "NSub", "curDur"))
  }
}

```


```{r}
mpredY_sub$RP_bias = mpredY_sub$m_repDur -mpredY_sub$curDur
mpredY_sub_new <- dplyr::group_by(mpredY_sub, curDur, Exp, NSub) %>%
  dplyr::summarize(m_RP_bias = mean(RP_bias))%>% spread(curDur, m_RP_bias)
mpredY_sub_WMsize <- dplyr::group_by(mpredY_sub, WMSize, Exp, NSub) %>%
  dplyr::summarize(m_RP_bias = mean(RP_bias))%>% spread(WMSize, m_RP_bias)
```


```{r message=FALSE}
#### predicted data
m_predY <- mpredY_sub%>% 
  dplyr::group_by(Exp, curDur, WMSize) %>% 
  dplyr::summarize(m_m_repDur = mean(m_repDur),
                   m_sd_repDur = mean(sd_repDur),
                   m_m_sig_r =mean(m_sig_r),
                   m_m_mu_r = mean(m_mu_r),
                   m_m_wp = mean(m_wp),
                   n = n(),
                   m_se_wp = sd(se_wp)/sqrt(n-1),
                   log_lik =mean(log_lik),
                   mpredRP_err = mean(predRP_err),
                   mpredVar_err = mean(predVar_err),
                   mpredRP_rerr = mean(predRP_rerr),
                   mpredVar_rerr = mean(predVar_rerr),
                   cv= mean(cv),
                   pred_cv = mean(pred_cv),
                   mpredcv_err = mean(predcv_err),
                   mpredcv_rerr = mean(predcv_rerr))
m_predY_acc =  mpredY_sub%>% 
  dplyr::group_by(Exp) %>% 
  dplyr::summarize(mpred_rerr = mean(predRP_rerr)*100,
                   mpredVar_rerr = mean(predVar_rerr)*100, 
                   mpredcv_rerr = mean(predcv_rerr)*100)
m_predY_acc
```


# WAIC and LOO-CV
```{r}
#extract waic and loo-cv from parameter list
m_WAIC <- dplyr::group_by(Bayparlist, Exp) %>%
  dplyr::summarize(n =n(),
                   m_looic = mean(looic),
                   m_waic = mean(waic),
                   se_waic = sd(waic)/sqrt(n-1),
                   se_looic = sd(looic)/sqrt(n-1),
                   m_p_loo = mean(p_loo),
                   m_elpd_loo = mean(elpd_loo),
                   m_se_looic = mean(se_looic),
                   m_se_p_loo = mean(se_p_loo),
                   m_p_waic = mean(p_waic),
                   m_se_waic = mean(se_waic)) 

m_WAIC
```




```{r}
#load test results
AllDat_newY <- read.csv(paste0(modelPath, "/rlt/AllDat_newY_",modelversion,".csv"))
AllDat_newY$WMSize <- as.factor(AllDat_newY$WMSize)
levels(AllDat_newY$WMSize) = c("low", "medium",  "high")
```

```{r include=FALSE}
m_newY <- dplyr::group_by(AllDat_newY, Exp, curDur, WMSize) %>%
  dplyr::summarize(m_mu_r = mean(mu_r),
                   m_sig_r = mean(sig_r),
                   log_lik =mean(log_lik)
  )
```


# Plot Results 

## RP

```{r}
RP  <- ggplot(data = m_predY, aes(x = curDur, y = m_m_repDur,  color=WMSize, shape = as.factor('Observation'))) +
  geom_point(size=2, alpha = 0.5)+
  geom_line(data= m_newY, aes(x=curDur, y=m_mu_r, color=WMSize)) +
  #geom_point(data = m_predY, aes(x = curDur, y = m_m_predY, color=WMSize, group = WMSize, shape = as.factor('Prediction')),alpha = 0.5)+
  geom_abline(slope=1, intercept=0)+
  facet_grid(cols = vars(Exp)) +
  labs(x="Sample intervals (s)", y="Reproduction (s)", shape=" ", color = "Memory Load")+
  theme_new+colorSet3+guides(shape="none")

RP
```



##  RP Slope
```{r}
# calculate the slope of the cv curve
RPslope_model <- function(df) {
  lm(m_repDur ~ log(curDur), data = df)
}

RPslopes <- mpredY_sub %>% 
  dplyr::group_by(NSub, Exp, WMSize) %>% nest() %>%
  mutate(model = map(data, RPslope_model)) %>% 
  mutate(slope = map(model, broom::tidy)) %>%  # get estimates
  unnest(slope, .drop = TRUE) %>% # remove raw data
  select(-std.error,-statistic, -p.value) %>%  # remove unnessary columns
  spread(term, estimate) %>%   # spread stimates
  dplyr::rename(Intercept = `(Intercept)`, slope = `log(curDur)`)  
RPslopes$data <- NULL
RPslopes$model <- NULL
```


```{r}
mRPslopes <- RPslopes%>% dplyr::group_by(WMSize, Exp) %>%
  dplyr::summarize(m_Intercept = mean(Intercept), 
                   m_slope = mean(slope),
                   n = n(), 
                   se_slope = sd(slope)/sqrt(n-1),
                   se_Intercept = sd(Intercept)/sqrt(n-1))

plt_CVslope <- ggplot(mRPslopes, aes(Exp, m_slope, ymin = m_slope - se_slope, ymax = m_slope + se_slope, group =interaction(Exp, WMSize), color = factor(WMSize)), shape = factor(WMSize))+ 
  geom_line(stat = "identity",position = position_dodge(width = 0.2))+
  geom_point(stat = "identity",position = position_dodge(width = 0.2))+ 
  geom_errorbar(width=.2,  position = position_dodge(width = 0.2)) +
  colorSet4+ 
  labs(x = "", y = TeX("Slope of RP"), color = 'Memory Load') +
  theme_new +theme(legend.position="top")

plt_CVslope

```


### Anova analysis on slopes of RP
```{r}
RPslopes$WMSize = as.factor(RPslopes$WMSize)
ezANOVA(data = RPslopes, dv= slope, wid=NSub, within=.(WMSize), between = .(Exp))
```

```{r}
ezANOVA(data = RPslopes %>% filter(Exp =='Exp1'), dv= slope, wid=NSub, within = .(WMSize))
```

```{r}
ezANOVA(data = RPslopes %>% filter(Exp =='Exp2'), dv= slope, wid=NSub, within = .(WMSize))

```

```{r}
ezANOVA(data = RPslopes %>% filter(Exp =='Exp3'), dv= slope, wid=NSub, within = .(WMSize))
```

```{r}
ezANOVA(data = RPslopes %>% filter(Exp =='Exp4'), dv= slope, wid=NSub, within = .(WMSize))
```

### Anova analysis on Intercept of RP
```{r}
ezANOVA(data = RPslopes, dv= Intercept, wid=NSub, within=.(WMSize), between = .(Exp))
```

## RP Bias

```{r}
RP_bias  <- ggplot(data = m_predY, aes(x = curDur, y = m_m_mu_r - curDur,color=WMSize, shape = as.factor('Observation'))) +
  geom_point(size=2, alpha = 0.5)+
  geom_line(data= m_newY, aes(x=curDur, y=m_mu_r-curDur, color=WMSize)) +
  geom_hline(yintercept = 0, linetype='dashed')+
  facet_grid(cols = vars(Exp)) +
  labs(x=" ", y="Reproduction bias (s)", shape=" ", color = "Memory Load")+theme_new+
  colorSet3+guides(shape="none")

RP_bias
```

## CV

```{r}
curDurItem <- unique(m_predY$curDur)
RP_CV <- ggplot(data= m_predY, aes(x=curDur, y= cv, color=WMSize, shape = as.factor('Observation'))) +
  geom_point(size=2, alpha = 0.5)+
  geom_line(data = m_newY, aes(x=curDur, y= m_sig_r/m_mu_r, color=WMSize)) +
  facet_grid(~Exp) +
  labs(x="Duration (s)", y="CV", shape=" ", color = "Memory Load")+ theme_new+
  colorSet3+guides(shape="none")+theme(strip.text.x = element_blank())
RP_CV
```

## CV slope

```{r}
# calculate the slope of the cv curve
cvSlope_model <- function(df) {
  lm(log(cv_obs) ~ log(curDur), data = df)
}

mpredY <- dplyr::group_by(AllDat_predY, curDur, WMSize, Exp, NSub) %>%
  dplyr::summarize(m_repDur = mean(repDur), 
                   sd_repDur = sd(repDur),
                   n = n(), 
                   sd_repDur = sd(repDur),
                   m_mu_r = mean(mu_r),
                   m_sig_r = mean(sig_r),
                   wp = mean(wp),
                   log_lik =mean(log_lik))
mpredY$cv_obs <- mpredY$sd_repDur/mpredY$m_repDur

CVslopes <- mpredY %>% 
  dplyr::group_by(NSub, Exp, WMSize) %>% nest()  %>%  # nested data
  mutate(model = map(data, cvSlope_model)) %>%  # linear regression
  mutate(slope = map(model, broom::tidy)) %>%  # get estimates
  unnest(slope, .drop = TRUE) %>% # remove raw data
  select(-std.error,-statistic, -p.value) %>%  # remove unnessary columns
  spread(term, estimate) %>%   # spread stimates
  dplyr::rename(obs_cv_Intercept = `(Intercept)`, obs_cv_slope = `log(curDur)`)  # rename columns
CVslopes$data = NULL
CVslopes$model = NULL
```

```{r}
#change the table struction of slopes for spss
CVslopes_list <-split(CVslopes, CVslopes$WMSize) 
CVslopes_spss = NULL
for (i in 1: length(CVslopes_list)){
  temp = CVslopes_list[[i]]
  WMSize = unique(temp$WMSize)
  temp$WMSize = NULL
  colnames(temp) = c('Exp',  'NSub', paste0('obs_cv_Intercept_',WMSize), paste0('obs_cv_slope_',WMSize))
  if(i == 1)
    CVslopes_spss = temp
  else
    CVslopes_spss = left_join(CVslopes_spss, temp, by=c("Exp",  "NSub"))
}
```



```{r}
mCVslopes <- CVslopes%>% dplyr::group_by(WMSize, Exp) %>%
  dplyr::summarize(n =n(),
                   m_obs_cv_Intercept = mean(obs_cv_Intercept), 
                   m_obs_cv_slope = mean(obs_cv_slope),
                   se_obs_CV_slope = sd(obs_cv_slope)/sqrt(n-1),
                   se_obs_CV_Intercept = sd(obs_cv_Intercept)/sqrt(n-1))
```



```{r}
plt_CVslope <- ggplot(mCVslopes, aes(Exp, m_obs_cv_slope, ymin = m_obs_cv_slope - se_obs_CV_slope, ymax = m_obs_cv_slope + se_obs_CV_slope, group =interaction(Exp, WMSize), color = factor(WMSize)), shape = factor(WMSize))+ 
  geom_line(stat = "identity",position = position_dodge(width = 0.2))+
  geom_point(stat = "identity",position = position_dodge(width = 0.2))+ 
  geom_errorbar(width=.2,  position = position_dodge(width = 0.2)) +
  colorSet4+ 
  labs(x = "", y = TeX("Slope of CV"), color = 'Memory Load') +
  theme_new +theme(legend.position="top")

plt_CVslope
```


```{r}
plt_CVIntecept<- ggplot(mCVslopes, aes(Exp, m_obs_cv_Intercept, ymin = m_obs_cv_Intercept - se_obs_CV_Intercept, ymax = m_obs_cv_Intercept + se_obs_CV_Intercept, group =interaction(Exp, WMSize), color = factor(WMSize)), shape = factor(WMSize))+ 
  geom_line(stat = "identity",position = position_dodge(width = 0.2))+
  geom_point(stat = "identity",position = position_dodge(width = 0.2))+ 
  geom_errorbar(width=.2,  position = position_dodge(width = 0.2)) +
  colorSet4+ 
  labs(x = "", y = TeX("Intercept of CV"), color = 'Memory Load') +
  theme_new +theme(legend.position="top")

plt_CVIntecept
```


```{r}
## Figures in the MS
fig_CV_slope_Intecept<-ggarrange(plt_CVslope, plt_CVIntecept, common.legend = TRUE, ncol=2, nrow=1,  labels = c("a", "b"))
#ggsave(paste0(getwd(), "/", modelPath, "/figures/fig_CV_slope_Intecept.png"), fig_CV_slope_Intecept, width = 8, height = 4)
fig_CV_slope_Intecept
```





```{r}
## Figures in the MS
fig3<-ggarrange(RP_bias, RP_CV, common.legend = TRUE, ncol=1, nrow=2,  labels = c("a", "b"))
ggsave(paste0(getwd(), "/", modelPath, "/figures/fig3.png"), fig3, width = 6, height = 5)
fig3
```

# Indifference Point

## Inifference Point (curve)

```{r}
AllDat_newY$predErr = AllDat_newY$mu_r - AllDat_newY$curDur

temp_newY <- AllDat_newY %>% filter(curDur > 0.8, curDur < 1.1) %>% select(Exp, WMSize, NSub, predErr, curDur)

InP_curve<- temp_newY%>% dplyr::group_by(Exp, WMSize, NSub)%>%
  dplyr::summarise(minErr = min(abs(predErr)), idx = which.min(abs(predErr)))
InP_curve$InP_curve = temp_newY[InP_curve$idx,]$curDur 
InP_curve
```


## Inifference Point (Equation)

```{r}
Bayparlist$wp_1 = (Bayparlist$sig_s2 + Bayparlist$ls *1 )/ (Bayparlist$sig_s2 + Bayparlist$ls *1 + Bayparlist$sig_pr2_log)

Bayparlist$wp_3 = (Bayparlist$sig_s2 + Bayparlist$ls *2) / (Bayparlist$sig_s2 + Bayparlist$ls *2 + Bayparlist$sig_pr2_log)

Bayparlist$wp_5 = (Bayparlist$sig_s2 + Bayparlist$ls *3) / (Bayparlist$sig_s2 + Bayparlist$ls *3 + Bayparlist$sig_pr2_log)

size = 1 
Bayparlist$InP_1 = exp((Bayparlist$kr*size + (1-Bayparlist$wp_1)*Bayparlist$ks*size + Bayparlist$wp_1* Bayparlist$mu_pr_log)/Bayparlist$wp_1)
size = 2
Bayparlist$InP_3 = exp((Bayparlist$kr*size + (1-Bayparlist$wp_3)*Bayparlist$ks*size + Bayparlist$wp_3* Bayparlist$mu_pr_log)/Bayparlist$wp_3)
size = 3
Bayparlist$InP_5 = exp((Bayparlist$kr*size + (1-Bayparlist$wp_5)*Bayparlist$ks*size + Bayparlist$wp_5* Bayparlist$mu_pr_log)/Bayparlist$wp_5)
```


```{r}
Bayparlist$sig2_post_1 = (Bayparlist$sig_pr2_log *(Bayparlist$sig_s2 +Bayparlist$ls*1))/(Bayparlist$sig_pr2_log + Bayparlist$sig_s2 +Bayparlist$ls*1) *0.5

Bayparlist$sig2_post_3 =(Bayparlist$sig_pr2_log *(Bayparlist$sig_s2 +Bayparlist$ls*3))/(Bayparlist$sig_pr2_log + Bayparlist$sig_s2 +Bayparlist$ls*3) *0.5 

Bayparlist$sig2_post_5 = (Bayparlist$sig_pr2_log *(Bayparlist$sig_s2 +Bayparlist$ls*5))/(Bayparlist$sig_pr2_log + Bayparlist$sig_s2 +Bayparlist$ls*5) *0.5

Bayparlist%>%filter(Exp == 'Exp2')%>%select("NSub", "Exp", "sig2_post_1", "sig2_post_3","sig2_post_5")

Bayparlist$InP_old_1 = exp((Bayparlist$kr*size - (1-Bayparlist$wp_1)*Bayparlist$ks*size +(Bayparlist$sig_pr2_log *(Bayparlist$sig_s2 +Bayparlist$ls*1))/(Bayparlist$sig_pr2_log + Bayparlist$sig_s2 +Bayparlist$ls*1) *0.5 + Bayparlist$wp_1* Bayparlist$mu_pr_log)/Bayparlist$wp_1)

Bayparlist$InP_old_3 = exp((Bayparlist$kr*size - (1-Bayparlist$wp_3)*Bayparlist$ks*size +(Bayparlist$sig_pr2_log *(Bayparlist$sig_s2 +Bayparlist$ls*3))/(Bayparlist$sig_pr2_log + Bayparlist$sig_s2 +Bayparlist$ls*3) *0.5 + Bayparlist$wp_3* Bayparlist$mu_pr_log)/Bayparlist$wp_3)

Bayparlist$InP_old_5 = exp((Bayparlist$kr*size - (1-Bayparlist$wp_5)*Bayparlist$ks*size +(Bayparlist$sig_pr2_log *(Bayparlist$sig_s2 +Bayparlist$ls*5))/(Bayparlist$sig_pr2_log + Bayparlist$sig_s2 +Bayparlist$ls*5) *0.5 + Bayparlist$wp_5* Bayparlist$mu_pr_log)/Bayparlist$wp_5)
```


```{r}
Bayparlist%>%select(NSub, Exp, wp_1, wp_3, wp_5, InP_1, InP_3, InP_5, InP_old_1, InP_old_3, InP_old_5)%>%
  unite(newcol1,  wp_1, InP_1, InP_old_1)%>%
  unite(newcol3,  wp_3, InP_3, InP_old_3)%>%
  unite(newcol5, wp_5, InP_5, InP_old_5)%>%
  melt(id.vars = c("NSub", "Exp")) %>%
  dplyr::rename(
    WMSize = variable,
    newcol = value
  )%>%
  separate(newcol,  c("wp", "InP_Eq", "InP_Eq_old"), sep = "_") -> Baypar_WMSize
Baypar_WMSize$WMSize <- substr(Baypar_WMSize$WMSize, 7, 7)
Baypar_WMSize$WMSize <- as.factor(Baypar_WMSize$WMSize)
Baypar_WMSize$InP_Eq = as.numeric(Baypar_WMSize$InP_Eq)
Baypar_WMSize$InP_Eq_old = as.numeric(Baypar_WMSize$InP_Eq_old)
levels(Baypar_WMSize$WMSize) = c("low", "medium",  "high")


##save csv for SPSS
left_join(Baypar_WMSize, InP_curve%>%select("Exp", "WMSize","NSub", "InP_curve"),  by = c("Exp","WMSize","NSub")) -> Baypar_WMSize

```


## check Indifferent Points 


```{r}
Baypar_WMSize_melt <- melt(Baypar_WMSize%>%select("Exp","WMSize","NSub", "InP_Eq", "InP_Eq_old", "InP_curve"), id.vars = c("Exp","WMSize","NSub"),
                           variable.name = "Type",
                           value.name = "InP" )


Baypar_WMSize_melt %>%filter(Type== "InP_curve") %>% dplyr::group_by(Exp)%>%
  dplyr::summarise(n = n(),
                   m_InP = mean(InP), se_InP= sd(InP)/sqrt(n-1))
```


```{r}
Baypar_WMSize_melt$Exp = as.factor(Baypar_WMSize_melt$Exp)

Baypar_WMSize_melt%>% dplyr::group_by(Exp, WMSize, Type)%>%
  dplyr::summarise(n = n(),
                   m_InP = mean(InP), se_InP= sd(InP)/sqrt(n-1))-> mBaypar_InP

```

```{r}
#plot InP_curve(the intersections of the Prediction curve with the diagonal)
plt_InP<- ggplot(data = mBaypar_InP%>%filter(Type== "InP_curve"), aes(x= Exp, y=m_InP, color = WMSize, shape = Type))+
  geom_line(stat = "identity",position = position_dodge(width = 0.2))+
  geom_point(stat = "identity",position = position_dodge(width = 0.2))+ 
  geom_errorbar(width=.2,  aes(ymin = m_InP - se_InP, ymax = m_InP + se_InP), position = position_dodge(width = 0.2)) +theme_new+
  labs(colour = "Memory Load")+colorSet3+
  xlab(' ')+ylab("Indifferent point (s)")+guides(shape="none")+
  theme(legend.position = "top")

plt_InP
```


##  anova on observed InP
```{r}
ezANOVA(data = Baypar_WMSize, dv= InP_curve, wid=NSub, within = .(WMSize), between = .(Exp))
```
```{r}
pairwise.t.test(Baypar_WMSize$InP_curve, Baypar_WMSize$Exp)
```


```{r}
ezANOVA(data = Baypar_WMSize %>% filter(Exp =='Exp2'), dv= InP_curve, wid=NSub, within = .(WMSize))
```

```{r}
ezANOVA(data = Baypar_WMSize %>% filter(Exp =='Exp3'), dv= InP_curve, wid=NSub, within = .(WMSize))
```

```{r}
ezANOVA(data = Baypar_WMSize %>% filter(Exp =='Exp4'), dv= InP_curve, wid=NSub, within = .(WMSize))
```

# Export data for spss

```{r}
### change the table struction for spss
Bayparlist_list <-split(Baypar_WMSize %>% select(c("NSub","Exp","WMSize", "wp","InP_curve")), Baypar_WMSize$WMSize) 
Bayparlist_spss = NULL
for (i in 1: length(Bayparlist_list)){
  temp = Bayparlist_list[[i]]
  WMSize = unique(temp$WMSize)
  temp$WMSize = NULL
  colnames(temp) = c('NSub','Exp', paste0('wp_',WMSize), paste0('InP_curve_',WMSize))
  if(i == 1)
    Bayparlist_spss = temp
  else
    Bayparlist_spss = left_join(Bayparlist_spss, temp, by=c("Exp",  "NSub"))
}

```



# anova analysis

## Anova on mean reproduction biases

```{r}
mpredY_sub$RP_Bias = mpredY_sub$m_repDur-mpredY_sub$curDur
RP_bias_Anova <- ezANOVA(data = mpredY_sub, dv= RP_Bias, wid=NSub, within= .(curDur, WMSize), between = .(Exp), detailed = TRUE, return_aov = FALSE )
RP_bias_Anova
```
```{r}
# main effect of Duration  F(1.177, 3.532) = 377.965, p < .001, ηp² = .863.
(RP_bias_Anova$ANOVA)$DFn[3] *(RP_bias_Anova$`Sphericity Corrections`)$GGe[1]
(RP_bias_Anova$ANOVA)$DFd[3] *(RP_bias_Anova$`Sphericity Corrections`)$GGe[1]
```


```{r}
#Duration × Experiment,  F(12, 240) = 2.506, p = .004, ηp² = .111
(RP_bias_Anova$ANOVA)$DFn[5] *(RP_bias_Anova$`Sphericity Corrections`)$GGe[2]
(RP_bias_Anova$ANOVA)$DFd[5] *(RP_bias_Anova$`Sphericity Corrections`)$GGe[2]
```

```{r}
mpredY_sub <- ungroup(mpredY_sub)
res.aov <-  rstatix::anova_test(data = mpredY_sub, dv = RP_Bias, wid = NSub, within = c(curDur, WMSize), between = Exp)
get_anova_table(res.aov, correction = "GG")
```

## variance of prior (anova)

```{r}
ezANOVA(data = Bayparlist, dv= sig_pr2_log, wid=NSub, between = .(Exp))
```
## variance of motor noise  (anova)
```{r}
ezANOVA(data = Bayparlist, dv= sig_mn2, wid=NSub, between = .(Exp))
```


## Ks anova

```{r}
ezANOVA(data = Bayparlist, dv= ks, wid=NSub, between = .(Exp))
```

##  mean of prior (anova)

```{r}
ezANOVA(data = Bayparlist, dv= mu_pr, wid=NSub, between = .(Exp))
```


# weight of prior

## Weight of the prior $w_p$

```{r}
Baypar_WMSize$wp = as.numeric(Baypar_WMSize$wp)
mwp <- Baypar_WMSize%>%dplyr::group_by(Exp, WMSize)%>% dplyr::summarise(m_wp = mean(wp), n= n(), se_wp = sd(wp)/sqrt(n-1))
plt_wp <- ggplot(mwp, aes(Exp, m_wp, ymin = m_wp - se_wp, ymax = m_wp + se_wp, group =interaction(Exp, WMSize), color = factor(WMSize)), shape = factor(WMSize))+ 
  geom_line(stat = "identity",position = position_dodge(width = 0.2))+
  geom_point(stat = "identity",position = position_dodge(width = 0.2))+ 
  geom_errorbar(width=.2,  position = position_dodge(width = 0.2)) +
  #coord_cartesian(ylim = c(0.5, 1)) +
  colorSet4+
  labs(x = "", y = TeX("Weight of the prior $w_p$"), color = 'Memory Load') +
  theme_new + theme(legend.position="top")

plt_wp
```

## combine InP and wp 



```{r}
fig4<-ggarrange(plt_wp, plt_InP, common.legend = TRUE, ncol=2, nrow=1,  labels = c("a", "b"))
#ggsave(paste0(getwd(), "/", modelPath, "/figures/fig4.png"), fig4, width = 6, height = 3)
fig4
```


## ANOVA analysis on wp

```{r}
ezANOVA(data = Baypar_WMSize, dv= wp, wid=NSub, within=.(WMSize), between = .(Exp))
```

```{r}
ezANOVA(data = Baypar_WMSize%>%filter(Exp =='Exp2'), dv= wp, wid=NSub, within= .(WMSize) )
```

```{r}
ezANOVA(data = Baypar_WMSize%>%filter(Exp =='Exp4'), dv= wp, wid=NSub, within= .(WMSize) )
```

```{r}
### pairwise.t.test on wp
pairwise.t.test(Baypar_WMSize$wp, Baypar_WMSize$Exp)
```


```{r}
##independent T test
t.test((Baypar_WMSize%>%filter(Exp %in%c('Exp1')))$wp)

t.test((Baypar_WMSize%>%filter(Exp %in%c('Exp2')))$wp)

t.test((Baypar_WMSize%>%filter(Exp %in%c('Exp3')))$wp)

t.test((Baypar_WMSize%>%filter(Exp %in%c('Exp4')))$wp)

```
## standard variance of Ds $\sigma_{s}$

```{r}
## One way ANOVA  on standard variance of Ds $\sigma_{s}$
ezANOVA(data = Bayparlist, dv= sig_s2, wid=NSub, between = .(Exp))
```


```{r}
### pairwise.t.test on standard variance of $D_s$
pairwise.t.test(Bayparlist$sig_s2, Bayparlist$Exp)
```


```{r}
##independent T test
t.test((Bayparlist%>%filter(Exp %in%c('Exp1')))$sig_s2)

t.test((Bayparlist%>%filter(Exp %in%c('Exp2')))$sig_s2)

t.test((Bayparlist%>%filter(Exp %in%c('Exp3')))$sig_s2)

t.test((Bayparlist%>%filter(Exp %in%c('Exp4')))$sig_s2)
```



## cv slope

```{r}
##  anova analyse on observed cv slope
ezANOVA(data = CVslopes, dv= obs_cv_slope, wid=NSub, between = .(Exp))
```


# Model prediction error

```{r}
m_predErr_sub<- mpredY_sub%>% 
  dplyr::group_by(Exp, WMSize, NSub) %>% dplyr::summarise(
    mpredRP_err=mean(predRP_err),
    mpredVar_err=mean(predVar_err),
    mpredcv_err = mean(predcv_err),
    mpredRP_rerr = mean(predRP_rerr),
    mpredVar_rerr = mean(predVar_rerr),
    mpredcv_rerr = mean(predcv_rerr))

m_predErr<- m_predY%>% 
  dplyr::group_by(Exp, WMSize) %>% dplyr::summarise(
    mmpredcv_err = mean(mpredcv_err),
    mmpredRP_err=mean(mpredRP_err),
    mmpredVar_err=mean(mpredVar_err),
    mmpredRP_rerr = mean(mpredRP_rerr),
    mmpredVar_rerr = mean(mpredVar_rerr),
    mmpredcv_rerr = mean(mpredcv_rerr))
m_predErr
```



# Model comparison (logarithmic vs. linear)

```{r}
m_predErr_sub$model = 'logarithmic'
m_predErr$model = 'logarithmic'
linear_model = 'linear'
m_predErr_linear = read.csv(paste0(getwd(), "/", rstanmodelPath, '/models/', linear_model, "/rlt/m_predErr_", linear_model, ".csv"))
m_predErr_linear$X = NULL
m_predErr_sub_linear = read.csv(paste0(getwd(), "/", rstanmodelPath, '/models/', linear_model, "/rlt/m_predErr_sub_", linear_model, ".csv"))
m_predErr_sub_linear$X = NULL

m_predErr_sub_all = rbind(m_predErr_sub, m_predErr_sub_linear) 
m_predErr_all = rbind(m_predErr, m_predErr_linear)
```

```{r}
m_predErr_all$WMSize = as.factor(m_predErr_all$WMSize)
levels(m_predErr_all$WMSize) =  c("low", "medium",  "high")
temp = m_predErr_all %>% filter(model == 'logarithmic') %>%summarise(abs_mmpredcv_err = abs(mmpredcv_err)) 

plt_Err_CV_all = ggplot(m_predErr_all, aes(abs(mmpredRP_err), abs(mmpredcv_err), group = interaction(model, Exp, WMSize), color = model, shape = Exp, size = WMSize)) + 
  geom_point() +
  geom_hline(yintercept = round(max(temp$abs_mmpredcv_err), 4)+0.0005, linetype='dashed')+
  xlab('Prediction error in the RP means (s)')+ ylab('Prediction error in CV')+colorSet3+
  scale_shape_manual(values = c(6, 7, 16, 17)) +
  theme_new+ 
  theme(legend.position = 'top')+
 labs(size = 'Memory Load')+
  guides(colour = guide_legend(order = 1, nrow=2,byrow=TRUE),
         shape = guide_legend(order =2, nrow=2,byrow=TRUE),
            size = guide_legend(order = 3, nrow=3,byrow=TRUE))

#ggsave(paste0(getwd(), "/", modelPath, "/figures/plt_Err_CV_all.png"), plt_Err_CV_all, width = 7, height = 4)

plt_Err_CV_all
```



```{r}
m_predY_acc =  m_predErr_sub_all%>% 
  dplyr::group_by(Exp, model) %>% 
  dplyr::summarize(mmpredRP_rerr = mean(mpredRP_rerr)*100,
                   mmpredVar_rerr = mean(mpredVar_rerr)*100,
                   mmpredcv_rerr = mean(mpredcv_rerr)*100,
                   mmpredRP_acc = (1-mean(mpredRP_rerr))*100,
                   mmpredVar_acc = (1-mean(mpredVar_rerr))*100,
                   mmpredCV_acc = (1-mean(mpredcv_rerr))*100)
m_predY_acc
```

