---
title: "behavioral results"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  
---

The raw data are stored in the subfolder `data`. Let's read in. 

```{r readdata, message=FALSE, warning=FALSE}
library(tidyverse)
library(MASS)
library(lme4)
library(lmerTest)
library(sjPlot)
raw = read.csv('../data/AllValidData.csv')
# experiment as a factor
raw$Exp = as.factor(raw$Exp)
# set unique subject No. and as a factor, SubNo. 10#, 20#...
raw$NSub = as.numeric(raw$Exp)*100 + raw$NSub

head(raw)
```

Visualize the mean reproduction biases. 

```{r meanplot, message=FALSE, warning=FALSE}
mRep = raw %>% filter(repDur > 0.2, repDur < 4) %>%
  group_by(Exp, NSub, WMSize, gap, curDur) %>% 
  summarise(Rep = mean(repDur)) %>%
  mutate(bias = Rep - curDur)

mmRep = mRep%>% #within-subject average 
  group_by(Exp, WMSize, gap, curDur) %>%
  summarise(mBias = mean(bias), se = sd(bias)/sqrt(n()), n = n())
mmRep$WMSize = as.factor(mmRep$WMSize)

mmRep$gap = as.factor(mmRep$gap)
# visualize the biases
ggplot(data = mmRep %>% filter(Exp == 'Exp5'), aes(curDur, mBias, linetype = gap, color = WMSize)) + 
  geom_point() + geom_line() + 
  geom_errorbar(aes(ymin = mBias - se, ymax = mBias + se), width = 0.1) +
  facet_wrap(~Exp) + theme_minimal()
```

Preliminary investigation using standard linear model to get first impression. 

```{r message=FALSE, warning=FALSE}
lm(Rep ~ Exp*curDur*WMSize,
            data = mRep %>% filter(Exp != 'Exp1') )
```

It seems that working memory impacts on the central tendency, as the interaction term WMSize x Duration varied across experiments. 

To make a formal analysis, we use linear mixed model. Given that Experiment 1 was a baseline checking the duration reproduciton was not impacted by the sequential presentation, we leave this experiment out for cross-experiment analysis. 

Given that we are interested how memory manipulation influence duration reproduction on the encoding and reproduction stages, the cross-experiment analysis mainly focuses on the manipulation stage. 

Here are the experimental design:

Exp. 2: Memory load on the encoding stage 
Exp. 3: Memory load on the reproduction stage
Exp. 4a (coded: 4): Memory load on both stages
Exp. 4b (coded: 5): Memory load on both stage + additional 2 sec gap. 

We are interested the following comparisons:
1. encoding vs. reproduction (Exp. 2 vs. Exp. 3)
2. individual impact vs. combination (exp. 2 + exp. 3 vs. Exp. 4a)
3. Gap effect (Exp. 4a vs. 4b )

Thus we construct the contrast matrix as follows:

$$\begin{equation*}
C = \begin{pmatrix}
1 & -1 & 0 & 0 \\
1 & 0 & -1 & 0 \\
0 & 0 & 1 & -1
\end{pmatrix}
\end{equation*}
$$
In addition, we assume in each experiment, the slope and intercept of the reproduction could be covaried across different memory loads for individuals. 

```{r lmm, message=FALSE, warning=FALSE}
# contrast among experiment. 
# we want to compare 
# 1. E2 vs E3 (encoding vs. reprod)
# 2. combination of two phases vs. spanning: E2 + E3 vs. E4a
# 3. gap: E4a vs. E4b

mRep$memory = (mRep$WMSize-1)/2  # memory load 0, 1, 2
mRep$cond = mRep$Exp #avoid confusion from output Exp --> Cond
mRep$duration = mRep$curDur - 1.1 # centered to 1.1 (middle point)

contr = rbind(c(1, -1, 0, 0), 
             c(1, 0, -1, 0),
             c(0, 0, 1, -1))
cmat = ginv(contr)

# Linear mixed model 
mod1 = lmer(bias ~ cond*duration*memory + 
              (duration * memory|NSub),  
            contrasts = list(cond = cmat), 
            data = mRep %>% filter(cond != 'Exp1'), REML = FALSE)
summary(mod1)
anova(mod1)
tab_model(mod1, digits = 3)
```




__Interpretation of the results__

* The overall central tendency across all experiments was significant.
The mean central tendency index was 0.45. 

* The main effect of Memory Load was also significant. Increase memory load one level elevated the bias for  22 ms. (Overestimation)

* There was no significant difference of mean central tendency effect for those comparisons we were interested in (the above three comparison). 

* Memory load, however, impacted differently. There was different impact of memory between Exp. 2 and 3., Exp2 + Exp 3 vs. Exp. 4. But there was no much difference between Exp 4 and 5 (4a vs. 4b)

* There was a strong interaction between memory and duration (central tendency). Increase one memory load level, the central tendency would increase 2.6% on average. 

* The impact of memory on central tendency significantly differ among three contrasts (comparisons). 
      1. Difference between Exp 2 vs. 3. 
      2. Exp. 4 differred from the combination of Exp. 2 and 3. (i.e., no complete cancel each other on the central tendency when memory load was imposed on both stages)
      3. Adding a gap inbetween increased 3.3% central tendency. 
      
      
### LMM for Exp. 4b
```{r}
mod4b = lmer(bias ~ gap*duration*memory + 
              (gap*duration*memory|NSub),  
            data = mRep %>% filter(Exp == 'Exp5'), REML = FALSE)
summary(mod4b)
anova(mod4b)
tab_model(mod4b, digits = 3)

```




