---
title: "Analyses for MS_Revision of WM_Reproduction"
author: "Jiao Wu"
date: "2023-09-21"
description: "adapted from behavioral_analysis.Rmd"
output: html_document:
    df_print: paged
    number_sections: true
  pdf_document: 
    number_sections: true
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages and functions {-}
```{r include=FALSE}
library(rlist)
library(ez)
library(tidyverse)
library(latex2exp)
library(lsr)
library(rticles)
library(DescTools)
library(heplots)
library(lme4)
library(rstatix)
library(boot)
library(ggpubr)
library(reshape2)
library(MASS)
library(lmerTest)
library(sjPlot)
```

```{r}
source('mytheme.R')
# model version
modelversion = 'gap_log_rstan'
rstanmodelPath = 'modelrlt'
modelPath = paste0(rstanmodelPath, '/models/', modelversion)
```

# omnibus analysis - Linear mixed model: Exp 2-5
```{r}
# data
raw = read.csv(paste0("../data/AllValidData.csv"))
# experiment as a factor
raw$Exp = as.factor(raw$Exp)
# set unique subject No. and as a factor, SubNo. 10#, 20#...
raw$NSub = as.numeric(raw$Exp)*100 + raw$NSub

mRep = raw %>% filter(repDur > 0.2, repDur < 4) %>%
  group_by(Exp, NSub, WMSize, gap, curDur) %>% 
  summarise(Rep = mean(repDur)) %>%
  mutate(bias = Rep - curDur)

mmRep = mRep%>% #within-subject average 
  group_by(Exp, WMSize, gap, curDur) %>%
  summarise(mBias = mean(bias), se = sd(bias)/sqrt(n()), n = n())
mmRep$WMSize = as.factor(mmRep$WMSize)
mmRep$gap = as.factor(mmRep$gap)

ggplot(data = mmRep, aes(curDur, mBias, color = WMSize)) + 
  geom_point() + geom_line() + 
  geom_errorbar(aes(ymin = mBias - se, ymax = mBias + se), width = 0.1) +
  facet_wrap(~Exp) + theme_minimal()

ggplot(data = mmRep %>% filter(Exp == 'Exp5'), 
       aes(curDur, mBias, linetype = gap, color = WMSize)) + 
  geom_point() + geom_line() + 
  geom_errorbar(aes(ymin = mBias - se, ymax = mBias + se), width = 0.1) +
  facet_wrap(~Exp) + theme_minimal()

```

```{r}
lm(Rep ~ Exp*curDur*WMSize,
            data = mRep %>% filter(Exp != 'Exp1') )
```

We are interested in the following comparisons:
1. encoding vs. reproduction (Exp. 2 vs. Exp. 3)
2. encoding vs. combination (Exp. 2 vs. Exp. 4)
3. Gap effect (Exp. 4 vs. 5)

Thus we construct the contrast matrix as follows:
$$\begin{equation*}
C = \begin{pmatrix}
1 & -1 & 0 & 0 \\
1 & 0 & -1 & 0 \\
0 & 0 & 1 & -1
\end{pmatrix}
\end{equation*}$$

```{r}
# contrast among experiment. 
# we want to compare 
# 1. E2 vs E3 (encoding vs. reprod)
# 2. E2 vs E4 (encoding vs. both phases)
# 3. gap: E4 vs. E5

mRep$memory = (mRep$WMSize-1)/2  # memory load 0, 1, 2
mRep$cond = mRep$Exp #avoid confusion from output Exp --> Cond
mRep$duration = mRep$curDur - 1.1 # centered to 1.1 (middle point)

contr = rbind(c(1, -1, 0, 0), 
             c(1, 0, -1, 0),
             c(0, 0, 1, -1))
cmat = ginv(contr)

# Linear mixed model 
mod1 = lmer(bias ~ cond*duration*memory + 
              (duration * memory|NSub),  
            contrasts = list(cond = cmat), 
            data = mRep %>% filter(cond != 'Exp1'), REML = FALSE)
summary(mod1)
anova(mod1)
tab_model(mod1, digits = 3)
```

# linear mixed model for the effect of holding period (gap) in Exp 5
```{r}
mod_Exp5 = lmer(bias ~ gap*duration*memory + 
              (gap*duration*memory|NSub),  
            data = mRep %>% filter(Exp == 'Exp5'), REML = FALSE)
summary(mod_Exp5)
anova(mod_Exp5)
tab_model(mod_Exp5, digits = 3)
```
# omnibus analysis - linear mixed model: Exp 6a-c
# 
```{r}
# data
Data_Exp6 <- read.csv(paste0("../data/Exp6.csv")) %>% filter(valid == 1)
Data_Exp6$Exp = as.factor(Data_Exp6$Exp)

mRep_Exp6 = Data_Exp6 %>% filter(repDur > 0.2, repDur < 4) %>%
  group_by(Exp, NSub, WMSize, curDur) %>% 
  summarise(Rep = mean(repDur)) %>%
  mutate(bias = Rep - curDur)

mmRep_Exp6 = mRep_Exp6 %>% #within-subject average 
  group_by(Exp, WMSize, curDur) %>%
  summarise(mBias = mean(bias), se = sd(bias)/sqrt(n()), n = n())
mmRep_Exp6$WMSize = as.factor(mmRep_Exp6$WMSize)

ggplot(data = mmRep_Exp6, aes(curDur, mBias, color = WMSize)) + 
  geom_point() + geom_line() + 
  geom_errorbar(aes(ymin = mBias - se, ymax = mBias + se), width = 0.1) +
  facet_wrap(~Exp) + theme_minimal()
```

We are interested in the following comparisons:
1. loading on encoding vs. reproduction (Exp. 6a vs. 6b)
2. loading on encoding vs. no load (exp. 6a vs. 6c)
3. loading on reproduction vs. no load (exp. 6b vs. 6c)

Thus we construct the contrast matrix as follows:

$$\begin{equation*}
C = \begin{pmatrix}
1 & -1 & 0 \\
1 & 0 & -1 \\
0 & 1 & -1
\end{pmatrix}
\end{equation*}$$

```{r lmm, message=FALSE, warning=FALSE}

mRep_Exp6$memory = (mRep_Exp6$WMSize-1)/2  # memory load 0, 1, 2
mRep_Exp6$cond = mRep_Exp6$Exp #avoid confusion from output Exp --> Cond
mRep_Exp6$duration = mRep_Exp6$curDur - 1.1 # centered to 1.1 (middle point)

contr_Exp6 = rbind(c(1, -1, 0), 
             c(1, 0, -1),
             c(0, 1, -1))
cmat_Exp6 = ginv(contr_Exp6)

# Linear mixed model 
mod_Exp6 = lmer(bias ~ cond*duration*memory + 
              (duration * memory|NSub),  
            contrasts = list(cond = cmat_Exp6), 
            data = mRep_Exp6, REML = FALSE)
summary(mod_Exp6)
anova(mod_Exp6)
tab_model(mod_Exp6, digits = 3)
```

